plyranges: a grammar of graphics for genomics data

### 2017-11-27 paper.Rmd
adding in outline for second paragraph

>>>>

# Design and Implementation

Discussion of the API and its key features

- every action on a Range is a verb (functional composition, method chaining)
- fluent (human readable, code describes what to do rather than 'how')
- every function returns a class familiar to the user
- an expressive algebra for performing arithmetic (anchoring functions)
- split-apply-combine strategies (group_by + reduce/summarise/mutate/filter)
- recasting overlapping/nearest etc as joins
